\addchap{Letter from the Editor}

 \initial{N}\emph{ew Annales} takes its name from the revolutionary Annales School of history. Rather than reaffirming the view that history is advanced by a few key individuals, the School sought to identify the underlying forces driving historical change. In answering some of the most important questions of our time, we draw inspiration from the Annales approach, and seek to situate our answers within a vastly more important question: where are we headed?

The pieces you will find in this issue are varied in theme and scope. The long-reads provide new perspectives on a few pressing questions. How should we, as individuals, approach global warming? Are we morally obligated to aid foreigners whose countries are halfway around the globe? If so, who should we aid first? 

The quick-takes tackle specific policy issues that we are now beginning to grapple with: whether we should legalise cannabis; how we should regulate genetic modification in babies; and how self-driving cars should operate in ethically-significant situations.

Finally, the reviews offer a glimpse into what our Members have been reading this semester: from Satya Nadella's memoir to a classic novel by Umberto Eco, they distill important insights about leadership, progress, and ethics.

This issue is the result of hundreds of hours of reading, reflecting, writing, and editing. I would like to personally thank our Members, our Board, and our editorial team: exceptional individuals without whom \emph{New Annales} would not have been realised.

Sincerely,

Laurent B\'elanger 